---
title: "Complete case outpatient predictive modeling with bootstrap"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
    code_folding: hide
editor_options:
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(here)
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(survival)
library(survminer)
library(StepReg)
library(caret)
library(pROC)
library(splitTools)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
path_raw <- fs::path("","Volumes","Peres_Research", "Myeloma", "Consortium Data", "May 2025")
path_save <- fs::path("","Volumes","Peres_Research", "Myeloma", "Analyses", "")

load(paste0(#path_raw, 
           here(), "/data",
           "/Cleaned_Consortium_Datasets_31Jul2025.RData"))
rm(combined_abecma, combined_iec, combined_aml)
```

This project aims to build a predictive model to identify low-risk CAR T patients that could be managed in the outpatient setting. I’ve provided some information on how to define the low-risk patients (the outcome) and potential predictors below.

Outcome
1 = patients with no CRS or grade 1 CRS, no ICANS, and no IEC-HS
0 = patients with grade 2 or higher CRS, patients with any ICANS, and patients with IEC-HS


```{r case cleaning}
combined_cart <- combined_cart %>% 
  # General
  # Fix letter case
  mutate(across(c(where(is.character),
                  -c("patientid",
                     "heavychain",
                     "bridging_response",
                     "r_iss", "updated_death_cause",
                     "eligible_cartitude1_reason",
                     contains("response"),
                     starts_with("ORR_"),
                     starts_with("CRorbetter")
                     )),
                ~ str_to_sentence(.) )) %>% 
  mutate(across(c("updated_death_cause", "Site"), 
                ~ str_to_lower(.)))
```


```{r general cleaning}
data1 <- combined_cart %>% 
  mutate(Site1 = str_replace_all(Site, " ", "_")) %>% 
  unite(col = patientid, c(cart_dataset, patientid, Site1), 
        sep = "-", 
        remove = FALSE) %>% 
  select(-Site1) %>% 
  # Fix numerical
  mutate_at(c("age_cart"
                  ), 
                ~ as.numeric(.)) %>%
  # Sex categories
  mutate(male_sex = case_when(
    sex == "Male"                                    ~ 1,
    sex == "Female"                                  ~ 0
  )) %>% 
  # ECOG
  mutate(ecog_apheresis_cat = case_when(
    ecog_apheresis == 0 |
      ecog_apheresis == 1                            ~ "0-1",
    ecog_apheresis %in% c(2:4)                       ~ "2-4"
  ), .after = ecog_apheresis) %>%
  mutate(ecog_at_ld_cat = case_when(
    ecog_ld == 0 |
      ecog_ld == 1                                   ~ "0-1",
    ecog_ld %in% c(2:4)                              ~ "2-4"
  ), .after = ecog_ld) %>%
  mutate_at(c("ecog_apheresis", "ecog_ld"), ~ factor(.)) %>% 
  # Cytogenetics ----
  mutate(cytogenetics = case_when(
    deletion_17p_tp53 == "Yes" | 
      t_414_yn == "Yes" | 
      t_1416_yn == "Yes"             ~ "Yes",
    deletion_17p_tp53 == "No" &
      t_414_yn == "No" &
      t_1416_yn == "No"               ~ "No",
    TRUE                                                           ~ NA_character_
  ), .before = deletion_17p_tp53) 
```

```{r therapy}
data1 <- data1 %>%
  # CART dose
  mutate(cart_infusion_dose = as.numeric(cart_infusion_dose)) %>% 
  mutate(cart_cell_dose_cat = case_when(
    cart_infusion_dose < 0.7                   ~ "< 0.7",
    cart_infusion_dose >= 0.7                  ~ "≥ 0.7"
  )) %>% 
  mutate(prior_tx_cat = case_when(
    prior_tx_lines <= 3                        ~ "1-3",
    prior_tx_lines <= 5                        ~ "4-5",
    prior_tx_lines >= 6                        ~ "≥6"
  ), prior_tx_cat = factor(prior_tx_cat, levels = 
                             c("1-3", "4-5", "≥6")
  )) %>% 
  mutate(condition_therapy = case_when(
    str_detect(str_to_lower(condition_therapy), "flu") &
      str_detect(str_to_lower(condition_therapy), "cy")       ~ "fludarabine + cytoxan",
    str_detect(str_to_lower(condition_therapy), "clad") &
      str_detect(str_to_lower(condition_therapy), "cy")       ~ "cladribine + cytoxan",
    TRUE                                                      ~ str_to_lower(condition_therapy)
  )) %>% 
  mutate(txhistory_priorbmca_list = case_when(
    txhistory_priorbmca_list == "None" |
      txhistory_priorbmca_list == "No" |
      txhistory_priorbmca_list == "N/a" |
      txhistory_priorbmca_list == "Na"         ~ NA_character_,
    TRUE                                       ~ txhistory_priorbmca_list
  )) %>% 
  # BCMA
  mutate(prior_bcma_therapy = case_when(
    !is.na(txhistory_priorbmca_list)           ~ "Yes",
    str_detect(
      str_to_upper(eligible_cartitude1_reason), 
      "BCMA")                                  ~ "Yes",
    str_detect(
      str_to_upper(eligible_cartitude1_reason), 
      "TECLISTAMAB")                           ~ "Yes",
    str_detect(
      str_to_upper(eligible_cartitude1_reason), 
      "TALQ")                                  ~ "Yes",
    
    is.na(txhistory_priorbmca_list)            ~ "No"
  )) %>% 
  # Lauren's updated code
  mutate(priorBCMA = case_when( # used a combination of prior therapy, bcma list, and ineligible for cartitude1 reason
    is.na(prior_other_therapy_yn) ~ NA_character_,
    str_detect(patientid, "Roswell28") ~ "No",
    str_detect(patientid, "12") & Site == "michigan"  ~ "No",
    prior_other_therapy_yn == "Yes" & txhistory_priorbmca_list == "Talquetamab" ~ "No",
    prior_other_therapy_yn == "Yes" & txhistory_priorbmca_list == "talq" ~ "No",
    prior_other_therapy_yn == "Yes" ~ "Yes",
    prior_other_therapy_yn == "No" & txhistory_priorbmca_list == "Teclistimab" ~ "Yes",
    prior_other_therapy_yn == "No" & txhistory_priorbmca_list == "Teneo biospeficic (TENIO 383B)" ~ "Yes",
    prior_other_therapy_yn == "No" ~ "No"
  )) %>% 

  mutate(bridging_response_prbetter = case_when(
    bridging_response == "Not Evaluable"       ~ NA_character_,
    str_detect(bridging_response, "CR|PR")     ~ "PR or better",
    bridging_yn == "No" & 
      is.na(bridging_response)                 ~ "No bridging",
    !is.na(bridging_response)                  ~ "< PR",
    is.na(bridging_response)                   ~ NA_character_,
    TRUE                                       ~ bridging_response
  ), .after = bridging_response
  ) %>% 
  mutate(bridging_response_prbetter = factor(
    bridging_response_prbetter, levels = c("No bridging", "< PR", "PR or better")
  ))


```

```{r toxicities}
data1 <- data1 %>% 
  # CRS
  # Remove NAs to duration and make as num
  mutate(crs_duration_days = as.numeric(crs_duration_days)) %>% 
  # Fix iec_hs_yn if updated_death_cause is HLH
  mutate(iec_hs_yn = case_when(
    # all HLH cause of death are not counted as iec, adding back
    str_detect(updated_death_cause, "hlh")          ~ "Yes",
    # not needed now but adding this line as warning for next update if it happens
    str_detect(updated_death_cause, "iec")          ~ "Yes",
    TRUE                                            ~ iec_hs_yn
  )) %>% 
  mutate(crs_outcome_detailled = case_when(
         (max_crs_grd == 0 |
            max_crs_grd == 1) &
            (max_icans_grd == 0 &
               iec_hs_yn == "No")                    ~ "Low - 1",
         (max_crs_grd == 0 |
            max_crs_grd == 1) &
            (is.na(max_icans_grd) |
               is.na(iec_hs_yn))                     ~ "no icans OR no iec data",
         
         (max_crs_grd == 0 |
            max_crs_grd == 1) &
            (max_icans_grd > 0 |
               iec_hs_yn == "Yes")                   ~ "Severe - 0",
         
         # (max_crs_grd == 1 &
         #   is.na(crs_duration_days)) &
         #    (max_icans_grd > 0 &
         #       iec_hs_yn == "Yes")                   ~ "Severe - 0",
         
         # (max_crs_grd == 1 &
         #   is.na(crs_duration_days))                 ~ "CRS 1 but no duration",
         
         # (max_crs_grd == 1 &
         #   crs_duration_days < 14) &
         #    (max_icans_grd == 0 &
         #       iec_hs_yn == "No")                    ~ "Low - 1",
         
         # (max_crs_grd == 1 &
         #   crs_duration_days < 14) &
         #    (is.na(max_icans_grd) |
         #       is.na(iec_hs_yn))                     ~ "no icans OR no iec data",
         
         max_crs_grd %in% c(2:5)                     ~ "Severe - 0",
         !is.na(max_crs_grd)                         ~ "check",
         TRUE                                        ~ NA_character_
       )) %>% 
  mutate(crs_outcome = factor(crs_outcome_detailled, levels = c("Severe - 0", "Low - 1")))

a <- data1 %>% select(patientid, max_crs_grd, crs_duration_days,crs_outcome, crs_outcome_detailled, max_icans_grd, iec_hs_yn, updated_death_cause)



```

```{r disease}
data2 <- data1 %>%
# Myeloma
  mutate(oligo_nonsecretory_chris = case_when(
    oligo_nonsecretory == "Non-secretory"        ~ "Yes",
    oligo_nonsecretory == "Oligosecretory"       ~ "Yes",
    TRUE                                             ~ oligo_nonsecretory
  ))
```

```{r baseline}
data2 <- data2 %>%
  mutate(bsln_bmpc_cat25 = case_when(
    bsln_bmpc < 25          ~ "bsln_bmpc < 25",
    bsln_bmpc >= 25         ~ "bsln_bmpc ≥ 25"
  )) %>% 
  mutate(bsln_bmpc_cat65 = case_when(
    bsln_bmpc < 65          ~ "bsln_bmpc < 65",
    bsln_bmpc >= 65         ~ "bsln_bmpc ≥ 65"
  )) %>% 
#   mutate(labs_platelets_preld = 
#            as.numeric(str_extract_all(labs_platelets_preld, "[[:digit:]]+"))
#   )  %>% 
  mutate(bsln_ferr_cat400 = case_when(
    labs_bsln_ferritin < 400          ~ "bsln_ferr < 400",
    labs_bsln_ferritin >= 400         ~ "bsln_ferr ≥ 400"
  )) %>% 
  mutate(bsln_crp_cat05 = case_when(
    labs_bsln_crp < 0.5          ~ "bsln_crp < 0.5",
    labs_bsln_crp >= 0.5         ~ "bsln_crp ≥ 0.5"
  )) %>% 
  mutate(ferritin_per200 = labs_bsln_ferritin / 200) %>% 
  mutate(cytopenia_preld = case_when(
    labs_anc_preld < 1.8 | 
      labs_hgb_preld < 11.4 | 
      labs_platelets_preld < 143                                ~ "Yes",
    is.na(labs_anc_preld) |
      is.na(labs_platelets_preld) |
      is.na(labs_hgb_preld)                               ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_preld = case_when(
    labs_anc_preld < 1 | 
      labs_hgb_preld < 8 | 
      labs_platelets_preld < 50                                        ~ "Yes",
    is.na(labs_anc_preld) |
      is.na(labs_platelets_preld) |
      is.na(labs_hgb_preld)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  
  
  mutate(cytopenia_d30 = case_when(
    labs_anc_d30 < 1.8 | 
      labs_hgb_d30 < 11.4 | 
      labs_platelets_d30 < 143                                ~ "Yes",
    is.na(labs_anc_d30) |
      is.na(labs_platelets_d30) |
      is.na(labs_hgb_d30)                               ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_d30 = case_when(
    labs_anc_d30 < 1 | 
      labs_hgb_d30 < 8 | 
      labs_platelets_d30 < 50                                        ~ "Yes",
    is.na(labs_anc_d30) |
      is.na(labs_platelets_d30) |
      is.na(labs_hgb_d30)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(cytopenia_d90 = case_when(
    labs_anc_d90 < 1.8 | 
      labs_hbg_d90 < 11.4 | 
      labs_platelets_d90 < 143                                ~ "Yes",
    is.na(labs_anc_d90) |
      is.na(labs_platelets_d90) |
      is.na(labs_hbg_d90)                               ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_d90 = case_when(
    labs_anc_d90 < 1 | 
      labs_hbg_d90 < 8 | 
      labs_platelets_d90 < 50                                        ~ "Yes",
    is.na(labs_anc_d90) |
      is.na(labs_platelets_d90) |
      is.na(labs_hbg_d90)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  ))
```

```{r EMD}
cilta <- data2 %>% 
  mutate(true_emd = case_when(
    extramedu_yn == "Yes" & 
      medhx_paraskeletal_yn == "No"              ~ "Yes", 
    extramedu_yn == "Yes" & 
      medhx_paraskeletal_yn == "Yes"             ~ "No",
    extramedu_yn == "No"                         ~ "No", 
    is.na(medhx_paraskeletal_yn)                 ~ NA_character_,
    TRUE                                         ~ "check"
  ))
a <- cilta %>% select(patientid, extramedu_yn, medhx_paraskeletal_yn, true_emd)
```


```{r Labeling}
# Labeling ----
var_label(cilta) <- list(age_cart = "Patient age", agecat = "Patient age - Categories",
                         male_sex = "Male Sex", sex = "Sex",
                         race_eth = "Race and ethnicity",
                         mo_os_from_infusion = "Follow-up time from infusion (months)",
                         extramedu_yn = "Extramedullary disease",
                         medhx_amyloid_yn = "Amyloidosis",
                         medhx_pcl_yn = "Plasma cell leukemia",
                         # circulating_plasma_cell = "UPDATED Circulating Plasma Cells",
                         bsln_burden_ge50pct = "High marrow burden (≥50%)",
                         ecog_ld = "ECOG at LD",
                         # `ECOG > or = 2? (Yes, No)` ,
                         r_iss = "R-ISS at cart infusion",
                         cytogenetics = "High risk cytogenetics (not include gain 1q)",
                         deletion_17p_tp53 = "Deletion 17p at Infusion",
                         t_414_yn = "t(4:14) at Infusion",
                         t_1416_yn = "t(4:16) at Infusion",
                         copyalteration_1q21 = "Gain/amp 1q21",
                         cytopenia_preld = "Cytopenia at pre LD",
                         gr3_cytopenia_preld = "Grade3 cytopenia at pre LD",
                         cytopenia_d30 = "Cytopenia at day30",
                         gr3_cytopenia_d30 = "Grade3 cytopenia at day30",
                         cytopenia_d90 = "Cytopenia at day90",
                         gr3_cytopenia_d90 = "Grade3 cytopenia at day90",
                         
                         # number_of_prior_lines_of_therapy = "Number of prior lines of therapy",
                         # number_prior_lines_therapy = "Number of prior lines of therapy (cat)",
                         prior_other_therapy_yn = "Prior other therapy",
                         bridging_yn = "Bridging therapy",
                         bridging_response = "Bridging response (detailled)",
                         bridging_response_prbetter = "Bridging response (PR or better)",
                         prior_auto_sct_yn = "Prior autoSCT",
                         prior_allo_sct_yn = "Prior alloSCT",
                         prior_tx_cat = "Number of prior regimens (cat)",
                         
                         condition_therapy = "Lymphodepletion chemotherapy",
                         priorBCMA = "Prior BCMA-directed therapy",
                         # need_for_g_csf_post_infus_yes_1_no_0 = "Granulocyte colony stimulating factor (G-CSF)",
                         # need_for_ivig_yes_1_no_0 = "Intravenous immunoglobulin (IVIG)",
                         # cd34_stem_cell_boost_yes_1_no_0 = "CD34 stem cell boost",
                         # tpo_agonist_post_cart_yes_1_no_0 = "Thrombopoietin (TPO) agonist",
                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese",
                         # steroid_use_yes_no = "Steroid Use", tocilizumab_yes_no = "Tocilizumab Use",
                         # anakinra_yes_no = "Anakinra Use",
                         proteasome = "Refractory to Proteasome Inhibitors",
                         # lenalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Lenalidomide",
                         # bortezomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Bortezomib",
                         # carfilzomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Carfilzomib",
                         # pomalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Pomalidomide",
                         dara = "Refractory to Daratumumab or Isatuximab",
                         immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
                         tripleref= "Triple refractory", pentaref= "Penta refractory",
                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese",
                         CRS_any = "Any CRS", CRS_gradecat = "CRS Grade",
                         ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade",
                         # day_of_onset_crs_relative_to_infusion = "Day of onset of CRS relative to infusion",
                         # day_of_max_crs_relative_to_infusion = "Day of Max CRS (relative to infusion)",
                         crs_duration_days = "Duration of CRS (days)",
                         # day_of_onset_icans_relative_to_infusion = "Day of onset of ICANS relative to infusion",
                         # day_of_max_icans_relative_to_infusion = "Day of Max ICANS (relative to infusion)",
                         icans_duration_days = "Duration of ICANS (days)",
                         # delayed_neuro = "Delayed Neurotoxicity",
                         # parkinsonian_neurotoxicity_yes_no = "Parkinsonian Neurotoxicity",
                         # other_delayed_non_parkinsonian_neurologic_toxicity_yes_no =
                         #   "Other/Delayed Non-Parkinsonian Neurologic Toxicity",
                         # delayed_neuro_type = "Delayed Neurotoxicity Type",
                         iec_hs_yn = "IEC-HS",
                         
                         ferritin_per200 = "Baseline Ferritin (scaled back 200)",

                         cart_infusion_days_from_aph = "Time from apheresis to CAR-T infusion (days)",
                         # total_dose_volume_m_l = "Total dose volume (mL)",
                         cart_infusion_dose = "Total cell dose (million cells)",
                         cart_cell_dose_cat = "Total cell dose (cat)",
                         # best_ORRcollapsed = "Best ORR at ≤ 12 months",


                         eligible_cartitude1 =
                           "Did patient meet cartitude criteria"#,
                         # best_response = "Best response in first 90 days"
)

```
<br>

<!-- # Exploratory analysis -->

```{r infused}
a <- data1 %>% 
  mutate(has_infusion_date = case_when(
    !is.na(cart_infusion_dt)          ~ "Yes",
    is.na(cart_infusion_dt)           ~ "No"
  )) %>% 
  select(patientid, infused_status, has_infusion_date, cart_infusion_days_from_aph)

cilta %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  # mutate(has_infusion_date = case_when(
  #   !is.na(cart_infusion_dt)          ~ "Yes",
  #   is.na(cart_infusion_dt)           ~ "No"
  # )) %>% 
  select(infused_status) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
```


```{r limit to infused patient}
cilta <- cilta %>% 
  filter(infused_status == "Infused")
```

<!-- ## We have `r nrow(cilta)` infused patients -->

# Predictive modeling

* Variables to consider:    
  + Age (age_cart)
  + Sex (sex)
  + Race and ethnicity (race_eth)
  + ECOG PS (ecog_ld, ecog_apheresis)
  + R-ISS disease stage (r_iss)
  + True EMD (extramed_yn)
  + Marrow burden – bone marrow plasma cell % (analyze both continuous and categorical - bsln_bmpc, bmpc_cat)
  + High-risk cytogenetics (any one of the del17p, t_414, t_1416 present, if missing some but no for others then = no, if missing all then missing)
  + Bridging therapy + response to bridging therapy (bridging_yn, bridging_therapy, bridging_response)
  + Penta-refractory status (pentaref)
  + Number of prior lines of therapy (prior_tx_lines, priortx_grp – may need to collapse groups if “1-3” doesn’t have many patients in one of the outcome groups).
  + Prior anti-BCMA therapy (prior_other_therapy_yn, txhistory_priorbmca_list)
  + Baseline CRP (labs_bsln_crp)
  + Baseline ferritin (labs_bsln_ferritin)


```{r remove NA in outcome}
limited_cilta <- cilta %>% 
  filter(!is.na(crs_outcome))
```

<!-- #### We have `r nrow(cilta)` infused patients with CRS outcome -->

```{r create limited data}
limited_cilta_with_ids <- limited_cilta %>% 
  select(patientid,
         age_cart, sex, 
         race_eth,
         ecog_at_ld_cat,
         ecog_ge_2,
         true_emd,
         bsln_bmpc, bmpc_cat,
         bsln_bmpc_cat25, bsln_bmpc_cat65,
         cytogenetics,
         bridging_yn, bridging_response_prbetter,
         pentaref, 
         prior_tx_lines, prior_tx_cat,
         priorBCMA,
         prior_other_therapy_yn,
         # cytopenia_preld,
         labs_bsln_crp, bsln_crp_cat05,
         labs_bsln_ferritin, bsln_ferr_cat400,
         eligible_cartitude1, crs_outcome)
limited_cilta <- limited_cilta_with_ids %>% 
  select(-patientid)
```

# Complete case data
```{r}
limited_cilta <- limited_cilta %>% 
  drop_na()
limited_cilta_with_ids <- limited_cilta_with_ids %>% 
  drop_na() %>% 
  # work around as paste0(limited_cilta_with_ids$patientid, collapse = "|")
  # remove more patients than planned
  mutate(keep_in_data = "Yes")
cilta <-
  inner_join(cilta,
             limited_cilta_with_ids %>% 
               select(patientid, keep_in_data))
```

<!-- # Population description -->
#### We have `r nrow(cilta)` infused patients with CRS outcome in the complete case dataset.

```{r}
cilta %>%
  select(Site) %>%
  tbl_summary() %>%
  bold_labels()
```

## Table 1. Patient characteristics (overall population considered)
```{r Table Patient characteristics}
cilta %>%
  select(#mo_os_from_infusion,
         age_cart, agecat, 
         male_sex, #sex,
         race_eth,
         # ecog_apheresis, ecog_apheresis_cat,
         ecog_at_ld_cat, #ecog_ld, ecog_ge_2,
         # subtype, r_iss,
         true_emd,
         # extramedu_yn, medhx_paraskeletal_yn,

         bsln_bmpc, bsln_bmpc_cat25, #bmpc_cat, bsln_bmpc_cat65,
         cytogenetics,
         # deletion_17p_tp53, t_414_yn, t_1416_yn,
         # copyalteration_1q21, deletion_1p32,
         medhx_pcl_yn,# medhx_amyloid_yn, 
         prior_tx_lines, #priortx_grp, #prior_other_therapy_yn,
         # immuno, proteasome, dara, 
         doubleref, tripleref, pentaref,
         # prior_auto_sct_yn, prior_allo_sct_yn,
         priorBCMA, #txhistory_priorbmca_list,
         bridging_yn,
         bridging_response_prbetter, #bridging_response, 
         condition_therapy,
         labs_bsln_crp, bsln_crp_cat05,
         labs_bsln_ferritin, bsln_ferr_cat400,
         cart_cell_dose_cat, #cart_infusion_dose, 
         eligible_cartitude1,
         crs_outcome
         ) %>%
  tbl_summary(by = crs_outcome,
    type = list(
      c(all_dichotomous()#ecog_ge_2,
        # true_emd,
        # cytogenetics,
        # deletion_17p_tp53,
        # t_414_yn,
        # t_1416_yn, copyalteration_1q21,
        # bridging_yn,
        # priorBCMA,
        # immuno, proteasome, dara, doubleref, tripleref, pentaref,
        # medhx_amyloid_yn, medhx_pcl_yn,
        # eligible_cartitude1
        )
      ~"categorical"),
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
    digits = all_continuous() ~ 1
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>%
  # add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(all_stat_cols() ~ "CRS outcome") %>%
  remove_footnote_header(columns = everything())
```

## Table 2. Clinical outcomes
```{r Table Clinical outcomes}
cilta %>%
  select(max_crs_grd,
         crs_duration_days,
         max_icans_grd,
         iec_hs_yn,
         other_neurotox_yn, parkinson_neurotox_yn,
         other_neurotox_cat, any_delay_neurotox_yn,
         nrm, nrm_grp,
         cytopenia_preld, gr3_cytopenia_preld,
         cytopenia_d30, gr3_cytopenia_d30,
         cytopenia_d90, gr3_cytopenia_d90,
         crs_outcome
         ) %>%
  tbl_summary(by = crs_outcome,
    type = list(
      c(all_dichotomous()
        )
      ~"categorical"),
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
    digits = all_continuous() ~ 1
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>%
  # add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(all_stat_cols() ~ "CRS outcome") %>%
  remove_footnote_header(columns = everything())
```

Cause of death within nrm groups
```{r}
cilta %>%
  filter(nrm_grp %in% c("Acute toxicity", "Delayed toxicity")) %>%
  select(nrm_grp, updated_death_cause) %>%
  tbl_summary(by = nrm_grp) %>%
  bold_labels() %>%
  modify_spanning_header(all_stat_cols() ~ "NRM group")
```

```{r}
cilta %>%
  filter(os_event == 1) %>% 
  select(crs_outcome, updated_death_cause) %>%
  mutate(updated_death_cause = case_when(
    updated_death_cause == "myeloma"                   ~ "Myeloma",
    updated_death_cause == "infection"	                   ~ "Infection",
    updated_death_cause == "unknown"	                   ~ "Unknown",
    updated_death_cause == "hlh"                   ~ "Acute toxicity",
    updated_death_cause == "colitis"                   ~ "Delayed toxicity",
    updated_death_cause == "crs"                   ~ "Acute toxicity",
    updated_death_cause == "icans"                   ~ "Acute toxicity",
    updated_death_cause == "iec-hs/hlh"	                   ~ "Acute toxicity",
    updated_death_cause == "hepatic gvhd"	                   ~ "Other",
    updated_death_cause == "infection secondary to iec-colitis"	    ~ "Infection",
    updated_death_cause == "nint"                   ~ "Delayed toxicity",
    updated_death_cause == "parkinsonism"                   ~ "Delayed toxicity",
    updated_death_cause == "spm"	                   ~ "SPM",
    updated_death_cause == "subdural hematoma"	                   ~ "Other"
  )) %>% 
  tbl_summary(by = crs_outcome, sort = everything() ~ "frequency") %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>%
  # add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(all_stat_cols() ~ "CRS outcome") %>%
  remove_footnote_header(columns = everything())


# a <- cilta %>% filter(os_event == 1) %>% 
#   select(updated_death_cause, nrm_grp)
```

## Table 3. Responses
```{r Table Responses}
cilta %>%
  select(day30_response, day30response, day30response_v2, day30response_MRD,
         mon3_response, mon3response, mon3response_v2, mon3response_MRD,
         mon6_response, mon6response, mon6response_v2, mon6response_MRD,
         mon9_response, mon9response, mon9response_v2, mon9response_MRD,
         mon12_response, mon12response, mon12response_v2, mon12response_MRD,
         best_response, best_response_MRD,
         best_ORR, best_CRorbetter,
         crs_outcome
         ) %>%
  tbl_summary(by = crs_outcome,
    type = list(
      c(all_dichotomous()
        )
      ~"categorical"),
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
    digits = all_continuous() ~ 1
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>%
  # add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(all_stat_cols() ~ "Responses") %>%
  remove_footnote_header(columns = everything())
```

## Survival
```{r}
ggsave_workaround <- function(g){
  survminer:::.build_ggsurvplot(x = g,
                                surv.plot.height = NULL,
                                risk.table.height = NULL,
                                ncensor.plot.height = NULL)}
```
### OS
Median OS
```{r}
survfit(Surv(mo_os_from_infusion, os_event) ~ 1, data = cilta)
survfit(Surv(mo_os_from_infusion, os_event) ~ crs_outcome, data = cilta)
```


```{r Survival analysis - KM by crs_outcome}
os_fig <- ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ crs_outcome,
                   data = cilta),
           # font.x = c(15, "bold", "black"),
           # font.y = c(15, "bold", "black"),
           font.legend = c(12, "plain", "black"),
           # font.tickslab = c(12, "bold", "black"),
           # size = 1.5,

           xlab = "Time (months)",
           ylab = "OS (probability)",
           legend = "top",
           legend.title = "Severe early toxicity", legend.labs = c("Yes", "No"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(nrow = 1))
os_fig
# ggsave("OS.tiff",
#        height = 5,
#        width = 8,
#        units = "in",
#        dpi = 600, compression = "lzw")
legend <- ggpubr::get_legend(os_fig)
# # Convert to a ggplot and print
legend <- ggpubr::as_ggplot(legend)
legend
# ggsave("KMs_legend.pdf",
#        width = 3,
#        height = 1,
#        dpi = 600)

myplot <-
  ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ crs_outcome,
                   data = cilta),
           # font.x = c(15, "bold", "black"),
           # font.y = c(15, "bold", "black"),
           font.legend = c(12, "plain", "black"),
           # font.tickslab = c(12, "bold", "black"),
           # size = 1.5,

           xlab = "Time (months)",
           ylab = "OS (probability)",
           legend = "none",
           legend.title = "Risk group", legend.labs = c("Severe", "Low"),
           pval = TRUE, pval.size = 4,
           conf.int = FALSE,
           risk.table = TRUE,
           risk.table.fontsize = 4,
           tables.y.text = FALSE, 
           tables.theme = theme_classic()+
             theme(text = element_text(size = 10),
                   # plot.title = element_text(size = 10),  # Table title ("Number at risk")
                   axis.text.x = element_text(size = 12),                # Time ticks (x-axis)
                   axis.title.y = element_text(size = 13), 
                   axis.title.x = element_text(size = 12)                # X-axis label ("Time")
             ),
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(nrow = 1))
myplot$table <- myplot$table + labs(y = "")

os_fig_table <- ggsave_workaround(myplot)

# ggsave("OS with risk table.tiff",
#        plot = os_fig_table,
#        height = 7,
#        width = 8,
#        units = "in",
#        dpi = 600, compression = "lzw")

coxph(Surv(time = cilta$mo_os_from_infusion,
                   event = cilta$os_event) ~ crs_outcome,
              data = cilta)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>% as_gt()
```

### PFS
Median PFS
```{r}
survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ 1, data = cilta)
survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ crs_outcome, data = cilta)
```

```{r PFS analysis - KM by crs_outcome}
pfs_fig <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ crs_outcome,
                   data = cilta),
           # font.x = c(15, "bold", "black"),
           # font.y = c(15, "bold", "black"),
           font.legend = c(12, "plain", "black"),
           # font.tickslab = c(12, "bold", "black"),
           # size = 1.5,

           xlab = "Time (months)",
           ylab = "PFS (probability)",
           legend = "top",
           legend.title = "Risk group", legend.labs = c("Severe", "Low"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(nrow = 1))
pfs_fig
# ggsave("PFS.tiff",
#        height = 5,
#        width = 8,
#        units = "in",
#        dpi = 600, compression = "lzw")

myplot <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ crs_outcome,
                   data = cilta),
           # font.x = c(15, "bold", "black"),
           # font.y = c(15, "bold", "black"),
           font.legend = c(12, "plain", "black"),
           # font.tickslab = c(12, "bold", "black"),
           # size = 1.5,

           xlab = "Time (months)",
           ylab = "PFS (probability)",
           legend = "none",
           legend.title = "Risk group", legend.labs = c("Severe", "Low"),
           pval = TRUE, pval.size = 4,
           conf.int = FALSE,
           risk.table = TRUE,
           risk.table.fontsize = 3,
           tables.y.text = FALSE,
           tables.theme = theme_classic()+
             theme(text = element_text(size = 10),
                   # plot.title = element_text(size = 10),  # Table title ("Number at risk")
                   axis.text.x = element_text(size = 12),                # Time ticks (x-axis)
                   axis.title.y = element_text(size = 13), 
                   axis.title.x = element_text(size = 12)                # X-axis label ("Time")
             ),
) %++% guides(colour = guide_legend(nrow = 1))
myplot$table <- myplot$table + labs(y = "")

pfs_fig_table <- ggsave_workaround(myplot)

# ggsave("PFS with risk table.tiff",
#        plot = pfs_fig_table,
#        height = 7,
#        width = 8,
#        units = "in",
#        dpi = 600, compression = "lzw")

coxph(Surv(time = cilta$mo_pfs_from_infusion,
                   event = cilta$pfs_event) ~ crs_outcome,
              data = cilta)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

# NRM
<!-- Cause of death within nrm groups -->
<!-- ```{r} -->
<!-- cilta %>% -->
<!--   # filter(nrm_grp %in% c("Acute toxicity", "Delayed toxicity")) %>% -->
<!--   select(nrm_grp, updated_death_cause) %>% -->
<!--   tbl_summary(by = nrm_grp) %>% -->
<!--   bold_labels() %>% -->
<!--   modify_spanning_header(all_stat_cols() ~ "NRM group") -->
<!-- ``` -->

```{r}
a <- cilta %>% filter(!is.na(nrm_grp)) %>% 
  select(patientid, nrm_grp, nrm, os_event, updated_death_cause, progression_dt) %>% 
  filter(nrm_grp %in% c("Other", "Spm"))

cilta <- cilta %>% 
  mutate(nrm = case_when(
    is.na(nrm) &
      updated_death_cause == "unknown"     ~ 1,
    !is.na(nrm)                            ~ nrm
  ))
```


```{r, fig.height=6}
nrm_fig <- ggsurvplot(survfit(Surv(mo_os_from_infusion, nrm) ~ crs_outcome,
                   data=cilta),
           fun = "event",
           # font.x = c(12, "plain", "black"),
           # font.y = c(12, "plain", "black"),
           font.legend = c(12, "plain", "black"),
           # font.tickslab = c(10, "plain", "black"),
           # size = 1.5,
           surv.median.line = "hv",

           xlab = "Time (months)",
           ylab = "Cumulative Incidence of NRM",
           legend = "top", 
           legend.title = "Risk group",
           legend.labs = c("Severe", "Low"),
           pval = TRUE, #pval.size = 4,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 3))
nrm_fig
# ggsave("Cumulative incidence.tiff",
#        height = 5,
#        width = 8,
#        units = "in",
#        dpi = 600, compression = "lzw")

myplot <- ggsurvplot(survfit(Surv(mo_os_from_infusion, nrm) ~ crs_outcome,
                   data=cilta),
           fun = "event",
           # font.main = c(20, "bold", "black"),
           # font.x = c(12, "plain", "black"),
           # font.y = c(12, "plain", "black"),
           font.legend = c(12, "plain", "black"),
           # font.tickslab = c(10, "plain", "black"),
           # size = 1.5,
           surv.median.line = "hv",

           xlab = "Time (months)",
           ylab = "Cumulative Incidence of NRM",
           legend = "none", legend.title = "Risk group",
           legend.labs = c("Severe", "Low"),
           pval = TRUE, pval.size = 4,
           conf.int = FALSE,
           risk.table = TRUE,
           risk.table.fontsize = 3,
           tables.y.text = FALSE,
           tables.theme = theme_classic()+
             theme(text = element_text(size = 10),
                   # plot.title = element_text(size = 10),  # Table title ("Number at risk")
                   axis.text.x = element_text(size = 12),                # Time ticks (x-axis)
                   axis.title.y = element_text(size = 13), 
                   axis.title.x = element_text(size = 12)                # X-axis label ("Time")
             ),
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 3))
myplot$table <- myplot$table + labs(y = "")
nrm_fig_table <- ggsave_workaround(myplot)

# ggsave("Cumulative incidence with risk table.tiff",
#        plot = myplot_fig,
#        height = 7,
#        width = 8,
#        units = "in",
#        dpi = 600, compression = "lzw")
```

```{r patchwork}
library(patchwork)

os_fig[["plot"]] /
  pfs_fig[["plot"]] /
  nrm_fig[["plot"]] + plot_annotation(tag_levels = 'A')+
  plot_layout(axis_titles = "collect", guides = "collect") &
  theme(plot.tag = element_text(size = 21),
        text = element_text(size = 13),
        legend.position = "bottom")
# ggsave("Curve panel figure_20260715.tiff",
#        height = 12,
#        width = 8,
#        units = "in",
#        dpi = 600, compression = "lzw")


# os_fig_table + pfs_fig_table + nrm_fig_table+
# plot_annotation(tag_levels = "A")+
#   plot_layout(axis_titles = "collect", guides = "collect") &
#   theme(plot.tag = element_text(size = 21),
#         text = element_text(size = 13),
#         axis.title = element_text(size = 15),
#         axis.text = element_text(size = 13), 
#         legend.position = "bottom",
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15))


# list(
#   ggsurvfit::ggsurvfit_build(os_fig_table),
#   ggsurvfit::ggsurvfit_build(pfs_fig_table),
#   ggsurvfit::ggsurvfit_build(nrm_fig_table)
# ) |> 
#   wrap_plots(nrow = 1) +
#   plot_annotation(tag_levels = "A"#, theme = theme(plot.margin = margin(t = 30))
#                   )+
#   plot_layout() &
#   theme(plot.tag = element_text(size = 21, margin = margin(t = -50)),
#         text = element_text(size = 13),
#         axis.title = element_text(size = 15),
#         axis.text = element_text(size = 13), 
#         plot.margin =  margin(t = 20),
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15))

list(
  ggsurvfit::ggsurvfit_build(os_fig_table),
  ggsurvfit::ggsurvfit_build(pfs_fig_table),
  ggsurvfit::ggsurvfit_build(nrm_fig_table)
) |> 
  wrap_plots(nrow = 1) /
  # (legend + theme(plot.margin = unit(c(-5,0,0,0), "cm"))
  #  ) +
  inset_element(legend, left = 0.3, bottom = 0, right = 0.7, top = -0.06, align_to = "full")+
  plot_annotation(tag_levels = list(c("A", "B", "C", NULL)))+
  plot_layout(axis_titles = "collect", guides = "collect") &
  theme(plot.tag = element_text(size = 21, margin = margin(t = -50)),
        text = element_text(size = 13),
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 13), 
        plot.margin =  margin(t = 20, b = 30),
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15))
# ggsave("Curve panel figure with table_20260715.tiff",
#        height = 6,
#        width = 13,
#        units = "in",
#        dpi = 600, compression = "lzw")

```






```{r select vars}
limited_cilta <- limited_cilta %>% 
  
  select(ecog_at_ld_cat,
         bsln_bmpc_cat25,
         # bsln_bmpc_cat65,
         # bsln_bmpc, 
         # bmpc_cat,
         cytogenetics,
         bridging_response_prbetter,
         pentaref, 
         bsln_crp_cat05,
         # labs_bsln_crp,
         # labs_bsln_ferritin, 
         bsln_ferr_cat400,
         crs_outcome)
```

# Stepwise regression / full cohort complete case
```{r stepwise regression, echo = TRUE, class.source= 'fold-hide'}
dat_df <- limited_cilta %>% 
    mutate(crs_outcome_glm = case_when(
    crs_outcome == "Severe - 0"      ~ 0,
    crs_outcome == "Low - 1"         ~ 1
  )) %>% 
  select(-crs_outcome) %>% 
  as.data.frame()

dat_factor <- dat_df %>% 
  mutate(crs_outcome_glm = factor(crs_outcome_glm, levels = c("0", "1")))

formula <- crs_outcome_glm ~ .
set.seed(1234)
res_complete_case <-
  stepwise(formula = formula,
           data = dat_factor,
           type = "logit",
           # include = "pentaref",
           strategy = "bidirection",
           metric = c("AIC", "SL"),
           sle=0.90,   #enters all since we already limited based on UVA
           sls=0.15)    # stays if pvalue < 0.10
res_complete_case
summary(res_complete_case$bidirection$AIC)
```


```{r}
report(res_complete_case, report_name = paste0(here::here(),
                                               "/Rmd/stepresults",
                                               "/stepwise_report_no_missing_bootval_", today()), format = "html")
```

Using the `r res_complete_case[["performance"]][["strategy:metric"]][1]` strategy, the voted model is   
`r res_complete_case[["performance"]][["model"]][1]`.   


## Modeling using complete cases data 
```{r,}
model_term <- res_complete_case[["performance"]][["model"]][1]
```
The final model is `r model_term`

```{r echo = TRUE, class.source= 'fold-hide'}
# Build original regression results to compare with bootstrap later
set.seed(123)
model_glm <- 
  glm(model_term, 
      data = dat_df, 
      family = "binomial")

reg_results <- model_glm %>% 
  tbl_regression(exponentiate=TRUE) %>% 
  bold_labels() %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
reg_results
```


# Bootstrap with boot()
Proceed with bootstrapping on our original data set for 1000 replicates.
```{r bootstrap validation with boot(), echo = TRUE, class.source= 'fold-show'}
# Bootstrap
library(Hmisc)
boot_reg <- function(data, index){
  model <- glm(model_term, family = binomial, 
           data = data[index,])
  # train
  return(coef(model))
}
library(boot)
set.seed(123)
boot_results <- boot(data = dat_df, statistic = boot_reg, R = 1000)
boot_results
```
<br>

## Estimate and CI correction
### Estimate correction
```{r get estimate correction, echo = TRUE, class.source= 'fold-show'}
original_estimates <- boot_results$t0 
calculated_bias <- colMeans(boot_results$t) - boot_results$t0 
bias_corrected_estimates <- original_estimates - calculated_bias 
print(bias_corrected_estimates)

cor_est <-
  exp(bias_corrected_estimates) %>% 
  as_tibble(rownames = "labels") %>% 
    filter(labels != "(Intercept)") %>% 
    mutate(labels = case_when(
      labels == "bsln_bmpc_cat25bsln_bmpc ≥ 25"            ~ "bsln_bmpc ≥ 25",
      labels == "bridging_response_prbetter< PR"           ~ "< PR",
      labels == "bridging_response_prbetterPR or better"   ~ "PR or better",
      labels == "bsln_ferr_cat400bsln_ferr ≥ 400"          ~ "bsln_ferr ≥ 400",
      labels == "ecog_at_ld_cat2-4"                        ~ "2-4",
      labels == "bsln_crp_cat05bsln_crp ≥ 0.5"             ~ "bsln_crp ≥ 0.5",
      labels == "cytogeneticsYes"                          ~ "Yes"
    ))
```

### CI correction
```{r get ci correction, echo = TRUE, class.source= 'fold-show'}
ci_bsln_bmpc_25 <- boot.ci(boot_results, type = "bca", index = 2)
ci_bsln_bmpc_25 <- exp(ci_bsln_bmpc_25[["bca"]][4:5])
ci_prbetter_PR <- boot.ci(boot_results, type = "bca", index = 3)
ci_prbetter_PR <- exp(ci_prbetter_PR[["bca"]][4:5])
ci_PR_better <- boot.ci(boot_results, type = "bca", index = 4)
ci_PR_better <- exp(ci_PR_better[["bca"]][4:5])
ci_bsln_ferr_400 <- boot.ci(boot_results, type = "bca", index = 5)
ci_bsln_ferr_400 <- exp(ci_bsln_ferr_400[["bca"]][4:5])
ci_ecog <- boot.ci(boot_results, type = "bca", index = 6)
ci_ecog <- exp(ci_ecog[["bca"]][4:5])
ci_crp <- boot.ci(boot_results, type = "bca", index = 7)
ci_crp <- exp(ci_crp[["bca"]][4:5])
ci_cyto <- boot.ci(boot_results, type = "bca", index = 8)
ci_cyto <- exp(ci_cyto[["bca"]][4:5])
cor_ci <-
  bind_rows(as_tibble(ci_bsln_bmpc_25, rownames = "label") %>% mutate(labels = "bsln_bmpc ≥ 25"), 
            as_tibble(ci_prbetter_PR, rownames = "label") %>% mutate(labels = "< PR"),
            as_tibble(ci_PR_better, rownames = "label") %>% mutate(labels = "PR or better"),
            as_tibble(ci_bsln_ferr_400, rownames = "label") %>% mutate(labels = "bsln_ferr ≥ 400"),
            as_tibble(ci_ecog, rownames = "label") %>% mutate(labels = "2-4"),
            as_tibble(ci_crp, rownames = "label") %>% mutate(labels = "bsln_crp ≥ 0.5"),
            as_tibble(ci_cyto, rownames = "label") %>% mutate(labels = "Yes")
  ) %>% 
  mutate(label = case_when(
    label == "1"         ~ "lower",
    label == "2"         ~ "upper",
  )) %>% 
  pivot_wider(id_cols = labels , 
              names_from = "label", 
              values_from = "value")

corrected_results <- 
  cor_est %>% 
  left_join(., cor_ci, by = "labels") %>% 
  mutate(OR_corrected = paste0("OR, ", round(value, 3), ", 95% CI, ", round(lower, 3), "-", round(upper, 3))) %>% 
  select(-c(value, lower, upper))
```
<br>

### Estimate and CI comparison table
```{r}
reg_results %>% 
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  mutate(N = case_when(
    !is.na(N)          ~ N,
    is.na(N)           ~ "label"
  )) %>% 
  mutate(OR_original = paste0("OR, ", OR, ", 95% CI, ", lower, "-", upper)) %>% 
  select(-c(OR, lower, upper, `p-value`)) %>% 
  mutate(OR_original = case_when(
    N == "label"                          ~ NA_character_,
    str_detect(OR_original, "NA-NA")      ~ "Reference",
    TRUE                                  ~ OR_original
  )) %>% 
  left_join(., corrected_results, by = c("Characteristic" = "labels")) %>% 
  mutate(N = case_when(
    N == "label"                          ~ NA_character_,
    TRUE                                  ~ N
  )) %>% 
  mutate(across(everything(), ~ replace_na(as.character(.x), ""))) %>% 
  kableExtra::kbl() %>% # Removes NAs locally
  kableExtra::kable_styling()
```


## AUC bootstrap
```{r bootstrap auc, echo = TRUE, class.source= 'fold-show'}
# Bootstrap
boot_auc <- function(data, index){
  data_ind <- data[index,]
  model <- glm(model_term, family = binomial, 
           data = data_ind)
  set.seed(123)
  predict_prob <- 
    predict(model_glm, newdata = data_ind, type = "response")
  predict_roc <- 
    roc(data_ind$crs_outcome_glm ~ predict_prob, plot = FALSE, print.auc = FALSE)
  
  return(as.numeric(predict_roc$auc))
}
library(boot)
set.seed(123)
boot_results <- boot(data = dat_df, statistic = boot_auc, R = 1000)
boot_results

original_estimates <- boot_results$t0 
calculated_bias <- colMeans(boot_results$t) - boot_results$t0 
bias_corrected_estimates <- original_estimates - calculated_bias 
# print(bias_corrected_estimates)
```


### AUC comparison
```{r comparison auc}
tibble(model = c("Original", "Bootstrap"),
       AUC = c(original_estimates,bias_corrected_estimates), .rows = )

```

### Figure AUC model built on full cohort
```{r auc, echo = TRUE, class.source= 'fold-show'}
set.seed(123)
model_glm <- 
  glm(model_term, 
      data = dat_df, 
      family = "binomial")
set.seed(123)
predict_prob <- 
  predict(model_glm, newdata = dat_df, type = "response")
# tiff("Figures/Train ROC_20260709.tiff", width = 6, height = 6, units = 'in', res = 300, type = "cairo", compression = 'lzw')
predict_roc <- 
  roc(dat_df$crs_outcome_glm ~ predict_prob, plot = TRUE, print.auc = TRUE)
# dev.off()
auc_value <- round(auc(predict_roc), 3)
ggroc(predict_roc, legacy.axes = TRUE, size = 1) +
  # Add the identity/diagonal reference line (equivalent to standard plot defaults)
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray") +
  
  # Print the AUC onto the plot (Replicates print.auc = TRUE)
  annotate("text", x = 0.4, y = 0.35, hjust = 0,
           label = paste0("Apparent AUC = ", auc_value), 
           size = 4, fontface = "plain") +
  annotate("text", x = 0.4, y = 0.3, hjust = 0,
           label = paste0("Optimism-corrected AUC = ", round(bias_corrected_estimates, 3)), 
           size = 4, fontface = "plain") +
  
  # Clean up axis labels and apply a clean theme
  labs(x = "False Positive Rate (1 - Specificity)",
       y = "True Positive Rate (Sensitivity)")

# ggsave("Figures/ROCAUC_20260715.tiff",
#        dpi = 600, units = "in",
#        width = 6,
#        height = 6, compression = "lzw"
#        )
```

### Figure Conf matrix model built on full cohort
```{r Conf matrix, echo = TRUE, class.source= 'fold-show'}
truth = dat_df$crs_outcome_glm

pred = ifelse(predict_prob > 0.5, "1", "0")

train_tab = table(predicted = pred, actual = truth)
train_con_mat = confusionMatrix(train_tab, positive = "1")
c(train_con_mat$overall["Accuracy"],
  train_con_mat$byClass["Sensitivity"],
  train_con_mat$byClass["Specificity"])
```

```{r}
conf_tab <- train_tab / rowSums(train_tab)
conf_tab <- as.data.frame(conf_tab, stringsAsFactors = TRUE)
conf_tab$actual <- factor(conf_tab$actual, rev(levels(conf_tab$actual)))

ggplot(conf_tab, aes(predicted, actual, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = scales::percent(Freq)), size = 3) +
  scale_fill_gradient(low = "white", high = "#3575b5")+
  labs(x = "Expected", y = "Predicted", 
       fill = "Overlap")+
  theme_classic()+
  theme(legend.position = "bottom")

# ggsave("Figures/Train confmetric_20260709.tiff",
#        dpi = 600, units = "in",
#        width = 6,
#        height = 6, compression = "lzw"
#        )
```




