---
title: "Response to reviewer"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
    code_folding: hide
editor_options:
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(here)
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(survival)
library(survminer)
library(StepReg)
library(caret)
library(pROC)
library(splitTools)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
path_raw <- fs::path("","Volumes","Peres_Research", "Myeloma", "Consortium Data", "May 2025")
path_save <- fs::path("","Volumes","Peres_Research", "Myeloma", "Analyses", "")

load(paste0(#path_raw, 
           here(), "/data",
           "/Cleaned_Consortium_Datasets_31Jul2025.RData"))
rm(combined_abecma, combined_iec, combined_aml)
```

<!-- This project aims to build a predictive model to identify low-risk CAR T patients that could be managed in the outpatient setting. I’ve provided some information on how to define the low-risk patients (the outcome) and potential predictors below. -->

<!-- Outcome -->
<!-- 1 = patients with no CRS or grade 1 CRS, no ICANS, and no IEC-HS -->
<!-- 0 = patients with grade 2 or higher CRS, patients with any ICANS, and patients with IEC-HS -->


```{r case cleaning}
combined_cart <- combined_cart %>% 
  # General
  # Fix letter case
  mutate(across(c(where(is.character),
                  -c("patientid",
                     "heavychain",
                     "bridging_response",
                     "r_iss", "updated_death_cause",
                     "eligible_cartitude1_reason",
                     contains("response"),
                     starts_with("ORR_"),
                     starts_with("CRorbetter")
                     )),
                ~ str_to_sentence(.) )) %>% 
  mutate(across(c("updated_death_cause", "Site"), 
                ~ str_to_lower(.)))
```


```{r general cleaning}
data1 <- combined_cart %>% 
  mutate(Site1 = str_replace_all(Site, " ", "_")) %>% 
  unite(col = patientid, c(cart_dataset, patientid, Site1), 
        sep = "-", 
        remove = FALSE) %>% 
  select(-Site1) %>% 
  # Fix numerical
  mutate_at(c("age_cart"
                  ), 
                ~ as.numeric(.)) %>%
  # Sex categories
  mutate(male_sex = case_when(
    sex == "Male"                                    ~ 1,
    sex == "Female"                                  ~ 0
  )) %>% 
  # ECOG
  mutate(ecog_apheresis_cat = case_when(
    ecog_apheresis == 0 |
      ecog_apheresis == 1                            ~ "0-1",
    ecog_apheresis %in% c(2:4)                       ~ "2-4"
  ), .after = ecog_apheresis) %>%
  mutate(ecog_at_ld_cat = case_when(
    ecog_ld == 0 |
      ecog_ld == 1                                   ~ "≤1",
    ecog_ld %in% c(2:4)                              ~ "≥2"
  ), .after = ecog_ld) %>%
  mutate_at(c("ecog_apheresis", "ecog_ld"), ~ factor(.)) %>% 
  # Cytogenetics ----
  mutate(cytogenetics = case_when(
    deletion_17p_tp53 == "Yes" | 
      t_414_yn == "Yes" | 
      t_1416_yn == "Yes"             ~ "High risk",
    deletion_17p_tp53 == "No" &
      t_414_yn == "No" &
      t_1416_yn == "No"               ~ "Standard risk",
    TRUE                                                           ~ NA_character_
  ), .before = deletion_17p_tp53) 
```

```{r therapy}
data1 <- data1 %>%
  # CART dose
  mutate(cart_infusion_dose = as.numeric(cart_infusion_dose)) %>% 
  mutate(cart_cell_dose_cat = case_when(
    cart_infusion_dose < 0.7                   ~ "< 0.7",
    cart_infusion_dose >= 0.7                  ~ "≥ 0.7"
  )) %>% 
  mutate(prior_tx_cat = case_when(
    prior_tx_lines <= 3                        ~ "1-3",
    prior_tx_lines <= 5                        ~ "4-5",
    prior_tx_lines >= 6                        ~ "≥6"
  ), prior_tx_cat = factor(prior_tx_cat, levels = 
                             c("1-3", "4-5", "≥6")
  )) %>% 
  mutate(condition_therapy = case_when(
    str_detect(str_to_lower(condition_therapy), "flu") &
      str_detect(str_to_lower(condition_therapy), "cy")       ~ "fludarabine + cytoxan",
    str_detect(str_to_lower(condition_therapy), "clad") &
      str_detect(str_to_lower(condition_therapy), "cy")       ~ "cladribine + cytoxan",
    TRUE                                                      ~ str_to_lower(condition_therapy)
  )) %>% 
  mutate(txhistory_priorbmca_list = case_when(
    txhistory_priorbmca_list == "None" |
      txhistory_priorbmca_list == "No" |
      txhistory_priorbmca_list == "N/a" |
      txhistory_priorbmca_list == "Na"         ~ NA_character_,
    TRUE                                       ~ txhistory_priorbmca_list
  )) %>% 
  # BCMA
  mutate(prior_bcma_therapy = case_when(
    !is.na(txhistory_priorbmca_list)           ~ "Yes",
    str_detect(
      str_to_upper(eligible_cartitude1_reason), 
      "BCMA")                                  ~ "Yes",
    str_detect(
      str_to_upper(eligible_cartitude1_reason), 
      "TECLISTAMAB")                           ~ "Yes",
    str_detect(
      str_to_upper(eligible_cartitude1_reason), 
      "TALQ")                                  ~ "Yes",
    
    is.na(txhistory_priorbmca_list)            ~ "No"
  )) %>% 
  # Lauren's updated code
  mutate(priorBCMA = case_when( # used a combination of prior therapy, bcma list, and ineligible for cartitude1 reason
    is.na(prior_other_therapy_yn) ~ NA_character_,
    str_detect(patientid, "Roswell28") ~ "No",
    str_detect(patientid, "12") & Site == "michigan"  ~ "No",
    prior_other_therapy_yn == "Yes" & txhistory_priorbmca_list == "Talquetamab" ~ "No",
    prior_other_therapy_yn == "Yes" & txhistory_priorbmca_list == "talq" ~ "No",
    prior_other_therapy_yn == "Yes" ~ "Yes",
    prior_other_therapy_yn == "No" & txhistory_priorbmca_list == "Teclistimab" ~ "Yes",
    prior_other_therapy_yn == "No" & txhistory_priorbmca_list == "Teneo biospeficic (TENIO 383B)" ~ "Yes",
    prior_other_therapy_yn == "No" ~ "No"
  )) %>% 

  mutate(bridging_response_prbetter = case_when(
    bridging_response == "Not Evaluable"       ~ NA_character_,
    str_detect(bridging_response, "CR|PR")     ~ "≥PR",
    bridging_yn == "No" & 
      is.na(bridging_response)                 ~ "No bridging",
    !is.na(bridging_response)                  ~ "< PR",
    is.na(bridging_response)                   ~ NA_character_,
    TRUE                                       ~ bridging_response
  ), .after = bridging_response
  ) %>% 
  mutate(bridging_response_prbetter = factor(
    bridging_response_prbetter, levels = c("No bridging", "< PR", "≥PR")
  ))


```

```{r toxicities}
data1 <- data1 %>% 
  # CRS
  # Remove NAs to duration and make as num
  mutate(crs_duration_days = as.numeric(crs_duration_days)) %>% 
  # Fix iec_hs_yn if updated_death_cause is HLH
  mutate(iec_hs_yn = case_when(
    # all HLH cause of death are not counted as iec, adding back
    str_detect(updated_death_cause, "hlh")          ~ "Yes",
    # not needed now but adding this line as warning for next update if it happens
    str_detect(updated_death_cause, "iec")          ~ "Yes",
    TRUE                                            ~ iec_hs_yn
  )) %>% 
  mutate(crs_outcome_detailled = case_when(
         (max_crs_grd == 0 |
            max_crs_grd == 1) &
            (max_icans_grd == 0 &
               iec_hs_yn == "No")                    ~ "Low - 1",
         (max_crs_grd == 0 |
            max_crs_grd == 1) &
            (is.na(max_icans_grd) |
               is.na(iec_hs_yn))                     ~ "no icans OR no iec data",
         
         (max_crs_grd == 0 |
            max_crs_grd == 1) &
            (max_icans_grd > 0 |
               iec_hs_yn == "Yes")                   ~ "Severe - 0",
         
         # (max_crs_grd == 1 &
         #   is.na(crs_duration_days)) &
         #    (max_icans_grd > 0 &
         #       iec_hs_yn == "Yes")                   ~ "Severe - 0",
         
         # (max_crs_grd == 1 &
         #   is.na(crs_duration_days))                 ~ "CRS 1 but no duration",
         
         # (max_crs_grd == 1 &
         #   crs_duration_days < 14) &
         #    (max_icans_grd == 0 &
         #       iec_hs_yn == "No")                    ~ "Low - 1",
         
         # (max_crs_grd == 1 &
         #   crs_duration_days < 14) &
         #    (is.na(max_icans_grd) |
         #       is.na(iec_hs_yn))                     ~ "no icans OR no iec data",
         
         max_crs_grd %in% c(2:5)                     ~ "Severe - 0",
         !is.na(max_crs_grd)                         ~ "check",
         TRUE                                        ~ NA_character_
       )) %>% 
  mutate(crs_outcome = factor(crs_outcome_detailled, levels = c("Severe - 0", "Low - 1")))

a <- data1 %>% select(patientid, max_crs_grd, crs_duration_days,crs_outcome, crs_outcome_detailled, max_icans_grd, iec_hs_yn, updated_death_cause)



```

```{r disease}
data2 <- data1 %>%
# Myeloma
  mutate(oligo_nonsecretory_chris = case_when(
    oligo_nonsecretory == "Non-secretory"        ~ "Yes",
    oligo_nonsecretory == "Oligosecretory"       ~ "Yes",
    TRUE                                             ~ oligo_nonsecretory
  ))
```

```{r baseline}
data2 <- data2 %>%
  mutate(bsln_bmpc_cat25 = case_when(
    bsln_bmpc < 25          ~ "< 25",
    bsln_bmpc >= 25         ~ "≥ 25"
  )) %>% 
  mutate(bsln_bmpc_cat65 = case_when(
    bsln_bmpc < 65          ~ "bsln_bmpc < 65",
    bsln_bmpc >= 65         ~ "bsln_bmpc ≥ 65"
  )) %>% 
#   mutate(labs_platelets_preld = 
#            as.numeric(str_extract_all(labs_platelets_preld, "[[:digit:]]+"))
#   )  %>% 
  mutate(bsln_ferr_cat400 = case_when(
    labs_bsln_ferritin < 400          ~ "< 400",
    labs_bsln_ferritin >= 400         ~ "≥ 400"
  )) %>% 
  mutate(bsln_crp_cat05 = case_when(
    labs_bsln_crp < 0.5          ~ "< 0.5",
    labs_bsln_crp >= 0.5         ~ "≥ 0.5"
  )) %>% 
  mutate(ferritin_per200 = labs_bsln_ferritin / 200) %>% 
  mutate(cytopenia_preld = case_when(
    labs_anc_preld < 1.8 | 
      labs_hgb_preld < 11.4 | 
      labs_platelets_preld < 143                                ~ "Yes",
    is.na(labs_anc_preld) |
      is.na(labs_platelets_preld) |
      is.na(labs_hgb_preld)                               ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_preld = case_when(
    labs_anc_preld < 1 | 
      labs_hgb_preld < 8 | 
      labs_platelets_preld < 50                                        ~ "Yes",
    is.na(labs_anc_preld) |
      is.na(labs_platelets_preld) |
      is.na(labs_hgb_preld)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  
  
  mutate(cytopenia_d30 = case_when(
    labs_anc_d30 < 1.8 | 
      labs_hgb_d30 < 11.4 | 
      labs_platelets_d30 < 143                                ~ "Yes",
    is.na(labs_anc_d30) |
      is.na(labs_platelets_d30) |
      is.na(labs_hgb_d30)                               ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_d30 = case_when(
    labs_anc_d30 < 1 | 
      labs_hgb_d30 < 8 | 
      labs_platelets_d30 < 50                                        ~ "Yes",
    is.na(labs_anc_d30) |
      is.na(labs_platelets_d30) |
      is.na(labs_hgb_d30)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(cytopenia_d90 = case_when(
    labs_anc_d90 < 1.8 | 
      labs_hbg_d90 < 11.4 | 
      labs_platelets_d90 < 143                                ~ "Yes",
    is.na(labs_anc_d90) |
      is.na(labs_platelets_d90) |
      is.na(labs_hbg_d90)                               ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_d90 = case_when(
    labs_anc_d90 < 1 | 
      labs_hbg_d90 < 8 | 
      labs_platelets_d90 < 50                                        ~ "Yes",
    is.na(labs_anc_d90) |
      is.na(labs_platelets_d90) |
      is.na(labs_hbg_d90)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  ))
```

```{r EMD}
cilta <- data2 %>% 
  mutate(true_emd = case_when(
    extramedu_yn == "Yes" & 
      medhx_paraskeletal_yn == "No"              ~ "Yes", 
    extramedu_yn == "Yes" & 
      medhx_paraskeletal_yn == "Yes"             ~ "No",
    extramedu_yn == "No"                         ~ "No", 
    is.na(medhx_paraskeletal_yn)                 ~ NA_character_,
    TRUE                                         ~ "check"
  ))
a <- cilta %>% select(patientid, extramedu_yn, medhx_paraskeletal_yn, true_emd)
```


```{r Labeling}
# Labeling ----
var_label(cilta) <- list(age_cart = "Patient age", agecat = "Patient age - Categories",
                         male_sex = "Male Sex", sex = "Sex",
                         race_eth = "Race and ethnicity",
                         mo_os_from_infusion = "Follow-up time from infusion (months)",
                         extramedu_yn = "Extramedullary disease",
                         medhx_amyloid_yn = "Amyloidosis",
                         medhx_pcl_yn = "Plasma cell leukemia",
                         # circulating_plasma_cell = "UPDATED Circulating Plasma Cells",
                         bsln_burden_ge50pct = "High marrow burden (≥50%)",
                         ecog_ld = "ECOG at LD",
                         # `ECOG > or = 2? (Yes, No)` ,
                         r_iss = "R-ISS at cart infusion",
                         cytogenetics = "High risk cytogenetics (not include gain 1q)",
                         deletion_17p_tp53 = "Deletion 17p at Infusion",
                         t_414_yn = "t(4:14) at Infusion",
                         t_1416_yn = "t(4:16) at Infusion",
                         copyalteration_1q21 = "Gain/amp 1q21",
                         cytopenia_preld = "Cytopenia at pre LD",
                         gr3_cytopenia_preld = "Grade3 cytopenia at pre LD",
                         cytopenia_d30 = "Cytopenia at day30",
                         gr3_cytopenia_d30 = "Grade3 cytopenia at day30",
                         cytopenia_d90 = "Cytopenia at day90",
                         gr3_cytopenia_d90 = "Grade3 cytopenia at day90",
                         
                         # number_of_prior_lines_of_therapy = "Number of prior lines of therapy",
                         # number_prior_lines_therapy = "Number of prior lines of therapy (cat)",
                         prior_other_therapy_yn = "Prior other therapy",
                         bridging_yn = "Bridging therapy",
                         bridging_response = "Bridging response (detailled)",
                         bridging_response_prbetter = "Bridging response (PR or better)",
                         prior_auto_sct_yn = "Prior autoSCT",
                         prior_allo_sct_yn = "Prior alloSCT",
                         prior_tx_cat = "Number of prior regimens (cat)",
                         
                         condition_therapy = "Lymphodepletion chemotherapy",
                         priorBCMA = "Prior BCMA-directed therapy",
                         # need_for_g_csf_post_infus_yes_1_no_0 = "Granulocyte colony stimulating factor (G-CSF)",
                         # need_for_ivig_yes_1_no_0 = "Intravenous immunoglobulin (IVIG)",
                         # cd34_stem_cell_boost_yes_1_no_0 = "CD34 stem cell boost",
                         # tpo_agonist_post_cart_yes_1_no_0 = "Thrombopoietin (TPO) agonist",
                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese",
                         # steroid_use_yes_no = "Steroid Use", tocilizumab_yes_no = "Tocilizumab Use",
                         # anakinra_yes_no = "Anakinra Use",
                         proteasome = "Refractory to Proteasome Inhibitors",
                         # lenalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Lenalidomide",
                         # bortezomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Bortezomib",
                         # carfilzomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Carfilzomib",
                         # pomalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Pomalidomide",
                         dara = "Refractory to Daratumumab or Isatuximab",
                         immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
                         tripleref= "Triple refractory", pentaref= "Penta refractory",
                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese",
                         CRS_any = "Any CRS", CRS_gradecat = "CRS Grade",
                         ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade",
                         # day_of_onset_crs_relative_to_infusion = "Day of onset of CRS relative to infusion",
                         # day_of_max_crs_relative_to_infusion = "Day of Max CRS (relative to infusion)",
                         crs_duration_days = "Duration of CRS (days)",
                         # day_of_onset_icans_relative_to_infusion = "Day of onset of ICANS relative to infusion",
                         # day_of_max_icans_relative_to_infusion = "Day of Max ICANS (relative to infusion)",
                         icans_duration_days = "Duration of ICANS (days)",
                         # delayed_neuro = "Delayed Neurotoxicity",
                         # parkinsonian_neurotoxicity_yes_no = "Parkinsonian Neurotoxicity",
                         # other_delayed_non_parkinsonian_neurologic_toxicity_yes_no =
                         #   "Other/Delayed Non-Parkinsonian Neurologic Toxicity",
                         # delayed_neuro_type = "Delayed Neurotoxicity Type",
                         iec_hs_yn = "IEC-HS",
                         
                         ferritin_per200 = "Baseline Ferritin (scaled back 200)",

                         cart_infusion_days_from_aph = "Time from apheresis to CAR-T infusion (days)",
                         # total_dose_volume_m_l = "Total dose volume (mL)",
                         cart_infusion_dose = "Total cell dose (million cells)",
                         cart_cell_dose_cat = "Total cell dose (cat)",
                         # best_ORRcollapsed = "Best ORR at ≤ 12 months",


                         eligible_cartitude1 =
                           "Did patient meet cartitude criteria"#,
                         # best_response = "Best response in first 90 days"
)

```
<br>

<!-- # Exploratory analysis -->


```{r limit to infused patient}
cilta <- cilta %>% 
  filter(infused_status == "Infused")
```

```{r remove NA in outcome}
limited_cilta <- cilta %>% 
  filter(!is.na(crs_outcome))
```

```{r create limited data}
limited_cilta_with_ids <- limited_cilta %>% 
  select(patientid,
         age_cart, sex, 
         race_eth,
         ecog_at_ld_cat,
         ecog_ge_2,
         true_emd,
         bsln_bmpc, bmpc_cat,
         bsln_bmpc_cat25, bsln_bmpc_cat65,
         cytogenetics,
         bridging_yn, bridging_response_prbetter,
         pentaref, 
         prior_tx_lines, prior_tx_cat,
         priorBCMA,
         prior_other_therapy_yn,
         # cytopenia_preld,
         labs_bsln_crp, bsln_crp_cat05,
         labs_bsln_ferritin, bsln_ferr_cat400,
         eligible_cartitude1, crs_outcome)
limited_cilta <- limited_cilta_with_ids %>% 
  select(-patientid)
```

```{r}
limited_cilta <- limited_cilta %>% 
  drop_na()
limited_cilta_with_ids <- limited_cilta_with_ids %>% 
  drop_na() %>% 
  # work around as paste0(limited_cilta_with_ids$patientid, collapse = "|")
  # remove more patients than planned
  mutate(keep_in_data = "Yes")
cilta <-
  inner_join(cilta,
             limited_cilta_with_ids %>% 
               select(patientid, keep_in_data))
```

#### We have `r nrow(cilta)` infused patients with CRS outcome in the complete case dataset.

```{r}
cilta <- cilta %>% 
  mutate(nrm = case_when(
    is.na(nrm) &
      updated_death_cause == "unknown"     ~ 1,
    !is.na(nrm)                            ~ nrm
  ))
```

```{r select vars}
limited_cilta <- limited_cilta %>% 
  
  select(ecog_at_ld_cat,
         bsln_bmpc_cat25,
         # bsln_bmpc_cat65,
         # bsln_bmpc, 
         # bmpc_cat,
         cytogenetics,
         bridging_response_prbetter,
         pentaref, 
         bsln_crp_cat05,
         # labs_bsln_crp,
         # labs_bsln_ferritin, 
         bsln_ferr_cat400,
         crs_outcome)
```

```{r stepwise regression}
dat_df <- limited_cilta %>% 
    mutate(crs_outcome_glm = case_when(
    crs_outcome == "Severe - 0"      ~ 0,
    crs_outcome == "Low - 1"         ~ 1
  )) %>% 
  select(-crs_outcome) %>% 
  as.data.frame()

dat_factor <- dat_df %>% 
  mutate(crs_outcome_glm = factor(crs_outcome_glm, levels = c("0", "1")))

formula <- crs_outcome_glm ~ .
set.seed(1234)
res_complete_case <-
  stepwise(formula = formula,
           data = dat_factor,
           type = "logit",
           # include = "pentaref",
           strategy = "bidirection",
           metric = c("AIC", "SL"),
           sle=0.90,   #enters all since we already limited based on UVA
           sls=0.15)    # stays if pvalue < 0.10
# res_complete_case
# summary(res_complete_case$bidirection$AIC)
```

<!-- Using the `r res_complete_case[["performance"]][["strategy:metric"]][1]` strategy, the voted model is    -->
<!-- `r res_complete_case[["performance"]][["model"]][1]`.    -->


<!-- ## Modeling using complete cases data  -->
```{r,}
model_term <- res_complete_case[["performance"]][["model"]][1]
```
The final model is  
`r model_term`

```{r}
dat_df <- dat_df %>% 
  # mutate(crs_outcome_glm = factor(crs_outcome_glm, levels = c("1", "0"))) %>% 
  mutate(bsln_bmpc_cat25 = factor(bsln_bmpc_cat25, levels = c("≥ 25", "< 25"))) %>% 
  mutate(bsln_ferr_cat400 = factor(bsln_ferr_cat400, levels = c("≥ 400", "< 400"))) %>% 
  mutate(ecog_at_ld_cat = factor(ecog_at_ld_cat, levels = c("≥2", "≤1"))) %>% 
  # mutate(bridging_response_prbetter = factor(bridging_response_prbetter, levels = c("PR or better", "No bridging", "< PR"))) %>% 
  mutate(bsln_crp_cat05 = factor(bsln_crp_cat05, levels = c("≥ 0.5", "< 0.5"))) %>% 
  mutate(cytogenetics = factor(cytogenetics, levels = c("High risk", "Standard risk")))
  
var_label(dat_df) <- list(bsln_bmpc_cat25 = "BM PC % at pre-LD", 
                         bsln_ferr_cat400 = "Baseline ferritin", 
                         cytogenetics = "Cytogenetic risk",
                         ecog_at_ld_cat = "ECOG at LD",
                         bsln_crp_cat05 = "Baseline CRP ",
                         bridging_response_prbetter = "Response to bridging therapy"
                         )

# Build original regression results to compare with bootstrap later
# set.seed(123)
# model_glm <- 
#   glm(model_term, 
#       data = dat_df, 
#       family = "binomial")
# 
# reg_results <- model_glm %>% 
#   tbl_regression(exponentiate=TRUE) %>% 
#   bold_labels() %>% 
#   bold_p(t = .05) %>% 
#   add_nevent(location = "level") %>% add_n(location = "level")

```


<!-- # Bootstrap with boot() -->
<!-- Proceed with bootstrapping on our original data set for 1000 replicates. -->
<!-- ```{r bootstrap validation with boot(), echo = TRUE, class.source= 'fold-show'} -->
<!-- # Bootstrap -->
<!-- library(Hmisc) -->
<!-- boot_reg <- function(data, index){ -->
<!--   model <- glm(model_term, family = binomial,  -->
<!--            data = data[index,]) -->
<!--   # train -->
<!--   return(coef(model)) -->
<!-- } -->
<!-- library(boot) -->
<!-- set.seed(123) -->
<!-- boot_results <- boot(data = dat_df, statistic = boot_reg, R = 1000) -->
<!-- boot_results -->
<!-- ``` -->
<!-- <br> -->

<!-- ## Estimate and CI correction -->
<!-- ### Estimate correction -->
<!-- ```{r get estimate correction, echo = TRUE, class.source= 'fold-show'} -->
<!-- original_estimates <- boot_results$t0  -->
<!-- calculated_bias <- colMeans(boot_results$t) - boot_results$t0  -->
<!-- bias_corrected_estimates <- original_estimates - calculated_bias  -->
<!-- print(bias_corrected_estimates) -->

<!-- cor_est <- -->
<!--   exp(bias_corrected_estimates) %>%  -->
<!--   as_tibble(rownames = "labels") %>%  -->
<!--     filter(labels != "(Intercept)") %>%  -->
<!--     mutate(labels = case_when( -->
<!--       labels == "bsln_bmpc_cat25bsln_bmpc ≥ 25"            ~ "bsln_bmpc ≥ 25", -->
<!--       labels == "bridging_response_prbetter< PR"           ~ "< PR", -->
<!--       labels == "bridging_response_prbetterPR or better"   ~ "PR or better", -->
<!--       labels == "bsln_ferr_cat400bsln_ferr ≥ 400"          ~ "bsln_ferr ≥ 400", -->
<!--       labels == "ecog_at_ld_cat2-4"                        ~ "2-4", -->
<!--       labels == "bsln_crp_cat05bsln_crp ≥ 0.5"             ~ "bsln_crp ≥ 0.5", -->
<!--       labels == "cytogeneticsYes"                          ~ "Yes" -->
<!--     )) -->
<!-- ``` -->

<!-- ### CI correction -->
<!-- ```{r get ci correction, echo = TRUE, class.source= 'fold-show'} -->
<!-- ci_bsln_bmpc_25 <- boot.ci(boot_results, type = "bca", index = 2) -->
<!-- ci_bsln_bmpc_25 <- exp(ci_bsln_bmpc_25[["bca"]][4:5]) -->
<!-- ci_prbetter_PR <- boot.ci(boot_results, type = "bca", index = 3) -->
<!-- ci_prbetter_PR <- exp(ci_prbetter_PR[["bca"]][4:5]) -->
<!-- ci_PR_better <- boot.ci(boot_results, type = "bca", index = 4) -->
<!-- ci_PR_better <- exp(ci_PR_better[["bca"]][4:5]) -->
<!-- ci_bsln_ferr_400 <- boot.ci(boot_results, type = "bca", index = 5) -->
<!-- ci_bsln_ferr_400 <- exp(ci_bsln_ferr_400[["bca"]][4:5]) -->
<!-- ci_ecog <- boot.ci(boot_results, type = "bca", index = 6) -->
<!-- ci_ecog <- exp(ci_ecog[["bca"]][4:5]) -->
<!-- ci_crp <- boot.ci(boot_results, type = "bca", index = 7) -->
<!-- ci_crp <- exp(ci_crp[["bca"]][4:5]) -->
<!-- ci_cyto <- boot.ci(boot_results, type = "bca", index = 8) -->
<!-- ci_cyto <- exp(ci_cyto[["bca"]][4:5]) -->
<!-- cor_ci <- -->
<!--   bind_rows(as_tibble(ci_bsln_bmpc_25, rownames = "label") %>% mutate(labels = "bsln_bmpc ≥ 25"),  -->
<!--             as_tibble(ci_prbetter_PR, rownames = "label") %>% mutate(labels = "< PR"), -->
<!--             as_tibble(ci_PR_better, rownames = "label") %>% mutate(labels = "PR or better"), -->
<!--             as_tibble(ci_bsln_ferr_400, rownames = "label") %>% mutate(labels = "bsln_ferr ≥ 400"), -->
<!--             as_tibble(ci_ecog, rownames = "label") %>% mutate(labels = "2-4"), -->
<!--             as_tibble(ci_crp, rownames = "label") %>% mutate(labels = "bsln_crp ≥ 0.5"), -->
<!--             as_tibble(ci_cyto, rownames = "label") %>% mutate(labels = "Yes") -->
<!--   ) %>%  -->
<!--   mutate(label = case_when( -->
<!--     label == "1"         ~ "lower", -->
<!--     label == "2"         ~ "upper", -->
<!--   )) %>%  -->
<!--   pivot_wider(id_cols = labels ,  -->
<!--               names_from = "label",  -->
<!--               values_from = "value") -->

<!-- corrected_results <-  -->
<!--   cor_est %>%  -->
<!--   left_join(., cor_ci, by = "labels") %>%  -->
<!--   mutate(OR_corrected = paste0("OR, ", round(value, 3), ", 95% CI, ", round(lower, 3), "-", round(upper, 3))) %>%  -->
<!--   select(-c(value, lower, upper)) -->
<!-- ``` -->
<!-- <br> -->

<!-- ### Estimate and CI comparison table -->
<!-- ```{r} -->
<!-- reg_results %>%  -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>%  -->
<!--   mutate(N = case_when( -->
<!--     !is.na(N)          ~ N, -->
<!--     is.na(N)           ~ "label" -->
<!--   )) %>%  -->
<!--   mutate(OR_original = paste0("OR, ", OR, ", 95% CI, ", lower, "-", upper)) %>%  -->
<!--   select(-c(OR, lower, upper, `p-value`)) %>%  -->
<!--   mutate(OR_original = case_when( -->
<!--     N == "label"                          ~ NA_character_, -->
<!--     str_detect(OR_original, "NA-NA")      ~ "Reference", -->
<!--     TRUE                                  ~ OR_original -->
<!--   )) %>%  -->
<!--   left_join(., corrected_results, by = c("Characteristic" = "labels")) %>%  -->
<!--   mutate(N = case_when( -->
<!--     N == "label"                          ~ NA_character_, -->
<!--     TRUE                                  ~ N -->
<!--   )) %>%  -->
<!--   mutate(across(everything(), ~ replace_na(as.character(.x), ""))) %>%  -->
<!--   kableExtra::kbl() %>% # Removes NAs locally -->
<!--   kableExtra::kable_styling() -->
<!-- ``` -->


<!-- ## AUC bootstrap -->
<!-- ```{r bootstrap auc, echo = TRUE, class.source= 'fold-show'} -->
<!-- # Bootstrap -->
<!-- boot_auc <- function(data, index){ -->
<!--   data_ind <- data[index,] -->
<!--   model <- glm(model_term, family = binomial,  -->
<!--            data = data_ind) -->
<!--   set.seed(123) -->
<!--   predict_prob <-  -->
<!--     predict(model_glm, newdata = data_ind, type = "response") -->
<!--   predict_roc <-  -->
<!--     roc(data_ind$crs_outcome_glm ~ predict_prob, plot = FALSE, print.auc = FALSE) -->

<!--   return(as.numeric(predict_roc$auc)) -->
<!-- } -->
<!-- library(boot) -->
<!-- set.seed(123) -->
<!-- boot_results <- boot(data = dat_df, statistic = boot_auc, R = 1000) -->
<!-- boot_results -->

<!-- original_estimates <- boot_results$t0  -->
<!-- calculated_bias <- colMeans(boot_results$t) - boot_results$t0  -->
<!-- bias_corrected_estimates <- original_estimates - calculated_bias  -->
<!-- # print(bias_corrected_estimates) -->
<!-- rm(boot_results) -->
<!-- ``` -->


<!-- ### AUC comparison -->
<!-- ```{r comparison auc} -->
<!-- tibble(model = c("Original", "Bootstrap"), -->
<!--        AUC = c(original_estimates,bias_corrected_estimates), .rows = ) -->

<!-- ``` -->

<!-- ### Figure AUC model built on full cohort -->
<!-- ```{r auc, echo = TRUE, class.source= 'fold-show'} -->
<!-- set.seed(123) -->
<!-- model_glm <-  -->
<!--   glm(model_term,  -->
<!--       data = dat_df,  -->
<!--       family = "binomial") -->
<!-- set.seed(123) -->
<!-- predict_prob <-  -->
<!--   predict(model_glm, newdata = dat_df, type = "response") -->
<!-- # tiff("Figures/Train ROC_20260709.tiff", width = 6, height = 6, units = 'in', res = 300, type = "cairo", compression = 'lzw') -->
<!-- predict_roc <-  -->
<!--   roc(dat_df$crs_outcome_glm ~ predict_prob, plot = TRUE, print.auc = TRUE) -->
<!-- # dev.off() -->
<!-- auc_value <- round(auc(predict_roc), 3) -->
<!-- ggroc(predict_roc, legacy.axes = TRUE, size = 1) + -->
<!--   # Add the identity/diagonal reference line (equivalent to standard plot defaults) -->
<!--   geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray") + -->

<!--   # Print the AUC onto the plot (Replicates print.auc = TRUE) -->
<!--   annotate("text", x = 0.4, y = 0.35, hjust = 0, -->
<!--            label = paste0("Apparent AUC = ", auc_value),  -->
<!--            size = 4, fontface = "plain") + -->
<!--   annotate("text", x = 0.4, y = 0.3, hjust = 0, -->
<!--            label = paste0("Optimism-corrected AUC = ", round(bias_corrected_estimates, 3)),  -->
<!--            size = 4, fontface = "plain") + -->

<!--   # Clean up axis labels and apply a clean theme -->
<!--   labs(x = "False Positive Rate (1 - Specificity)", -->
<!--        y = "True Positive Rate (Sensitivity)") -->

<!-- # ggsave("Figures/ROCAUC_20260715.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 6, -->
<!-- #        height = 6, compression = "lzw" -->
<!-- #        ) -->
<!-- ``` -->

<!-- ### Figure Conf matrix model built on full cohort -->
<!-- ```{r Conf matrix, echo = TRUE, class.source= 'fold-show'} -->
<!-- truth = dat_df$crs_outcome_glm -->

<!-- pred = ifelse(predict_prob > 0.5, "1", "0") -->

<!-- train_tab = table(predicted = pred, actual = truth) -->
<!-- train_con_mat = confusionMatrix(train_tab, positive = "1") -->
<!-- c(train_con_mat$overall["Accuracy"], -->
<!--   train_con_mat$byClass["Sensitivity"], -->
<!--   train_con_mat$byClass["Specificity"]) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- conf_tab <- train_tab / rowSums(train_tab) -->
<!-- conf_tab <- as.data.frame(conf_tab, stringsAsFactors = TRUE) -->
<!-- conf_tab$actual <- factor(conf_tab$actual, rev(levels(conf_tab$actual))) -->

<!-- ggplot(conf_tab, aes(predicted, actual, fill = Freq)) + -->
<!--   geom_tile() + -->
<!--   geom_text(aes(label = scales::percent(Freq)), size = 3) + -->
<!--   scale_fill_gradient(low = "white", high = "#3575b5")+ -->
<!--   labs(x = "Expected", y = "Predicted",  -->
<!--        fill = "Overlap")+ -->
<!--   theme_classic()+ -->
<!--   theme(legend.position = "bottom") -->

<!-- # ggsave("Figures/Train confmetric_20260709.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 6, -->
<!-- #        height = 6, compression = "lzw" -->
<!-- #        ) -->
<!-- ``` -->

# I. Identify thresholds/sensitivity/specificity using the full cohort
## A. Identify the threshold that maximizes the combined sensitivity + specificity
```{r echo = TRUE, class.source= 'fold-hide'}
model_glm <- 
  glm(model_term, 
      data = dat_df, 
      family = "binomial")
predict_prob <- 
  predict(model_glm, newdata = dat_df, type = "response")
# Change quiet = TRUE
predict_roc <- 
  roc(dat_df$crs_outcome_glm ~ predict_prob, quiet = TRUE)

best_youden <- pROC::coords(
  predict_roc,
  x = "best",
  best.method = "youden",
  ret = c("threshold", "sensitivity", "specificity"),
  transpose = FALSE
)
best_youden
```



```{r echo = TRUE, class.source= 'fold-hide'}
model_glm <- 
  glm(model_term, 
      data = dat_df, 
      family = "binomial")
predict_prob <- 
  predict(model_glm, newdata = dat_df, type = "response")
# Change quiet = TRUE
predict_roc <- 
  roc(dat_df$crs_outcome_glm ~ predict_prob, quiet = TRUE)

roc_coords <- pROC::coords(
  predict_roc,
  x = "all",
  ret = c("threshold", "sensitivity", "specificity"),
  transpose = FALSE
)
roc_coords
```

## B. Identifying under a pre-specified minimum specificity of 90% and selecting thresholds with the highest sensitivity.
```{r echo = TRUE, class.source= 'fold-hide'}
# Require specificity ≥ 0.90
candidate <- roc_coords[roc_coords$specificity >= 0.90, ]
# Among those thresholds, maximize sensitivity
optimal <- candidate[which.max(candidate$sensitivity), ]
optimal
```

## C. Identifying under a pre-specified minimum specificity of 95% and selecting thresholds with the highest sensitivity.
```{r echo = TRUE, class.source= 'fold-hide'}
# Require specificity ≥ 0.90
candidate <- roc_coords[roc_coords$specificity >= 0.95, ]
# Among those thresholds, maximize sensitivity
optimal <- candidate[which.max(candidate$sensitivity), ]
optimal
```
<br>

# II. Identify thresholds/sensitivity/specificity using bootstrapping on our original data set for 1000 replicates.
## A. Identify the threshold that maximizes the combined sensitivity + specificity
```{r echo = TRUE, class.source= 'fold-hide'}
# Bootstrap
boot_thresh <- function(data, index) {
  # Bootstrap sample
  data_ind <- data[index, ]
  # Fit logistic regression
  model_glm_boot <- glm(
    model_term,
    family = binomial,
    data = data_ind
  )
  # Predicted probabilities
  predict_prob <- predict(model_glm_boot, newdata = data_ind, type = "response")
  # ROC curve
  predict_roc <- pROC::roc(response = data_ind$crs_outcome_glm, predictor = predict_prob, quiet = TRUE)
  # Get Youden optimum
  best_youden <- pROC::coords(
    predict_roc,
    x = "best",
    best.method = "youden",
    ret = c("threshold", "sensitivity", "specificity"),
    transpose = FALSE
  )
  
  # Force first optimal threshold
  threshold <- as.numeric(best_youden[["threshold"]][1])
  sensitivity <- as.numeric(best_youden[["sensitivity"]][1])
  specificity <- as.numeric(best_youden[["specificity"]][1])
  
  # Return EXACTLY 3 numbers
  c(
    threshold = threshold,
    sensitivity = sensitivity,
    specificity = specificity
  )
}

library(boot)

set.seed(123)
boot_results <- boot(data = dat_df, statistic = boot_thresh, R = 1000)
# boot_results

original_estimates <- boot_results$t0 
calculated_bias <- colMeans(boot_results$t) - boot_results$t0 
bias_corrected_estimates <- original_estimates - calculated_bias 
```

threshold/sensitivity/specificity comparison
```{r}
bind_rows(original_estimates,bias_corrected_estimates, .id = "model") |> 
  mutate(model = case_when(
    model == 1    ~ "Original",
    model == 2    ~ "Bootstrap"
  ))
```

## B. Identifying under a pre-specified minimum specificity of 90% and selecting thresholds with the highest sensitivity.
```{r}
# Bootstrap
boot_thresh <- function(data, index) {
  # Bootstrap sample
  data_ind <- data[index, ]
  # Fit logistic regression
  model_glm_boot <- glm(
    model_term,
    family = binomial,
    data = data_ind
  )
  # Predicted probabilities
  predict_prob <- predict(model_glm_boot, newdata = data_ind, type = "response")
  # ROC curve
  predict_roc <- pROC::roc(response = data_ind$crs_outcome_glm, predictor = predict_prob, quiet = TRUE)
  # Get threshold requiring specificity ≥90%
  roc_coords <- pROC::coords(
    predict_roc,
    x = "all",
    ret = c("threshold", "sensitivity", "specificity"),
    transpose = FALSE
  )
  
  # Keep thresholds achieving ≥90% specificity
  candidate <- roc_coords[
    roc_coords$specificity >= 0.90,
  ]
  
  # Select threshold with highest sensitivity
  optimal_90 <- candidate[
    which.max(candidate$sensitivity),
  ]
  
  specificity90_threshold <- as.numeric(
    optimal_90[["threshold"]]
  )
  
  specificity90_sensitivity <- as.numeric(
    optimal_90[["sensitivity"]]
  )
  
  specificity90_specificity <- as.numeric(
    optimal_90[["specificity"]]
  )
  
  # Return EXACTLY 3 numbers
  c(
    specificity90_threshold = specificity90_threshold,
    specificity90_sensitivity = specificity90_sensitivity,
    specificity90_specificity = specificity90_specificity
  )
}

library(boot)

set.seed(123)
boot_results <- boot(data = dat_df, statistic = boot_thresh, R = 1000)
# boot_results

original_estimates <- boot_results$t0 
calculated_bias <- colMeans(boot_results$t) - boot_results$t0 
bias_corrected_estimates <- original_estimates - calculated_bias 
```

threshold/sensitivity/specificity comparison
```{r}
bind_rows(original_estimates,bias_corrected_estimates, .id = "model") |> 
  mutate(model = case_when(
    model == 1    ~ "Original",
    model == 2    ~ "Bootstrap"
  ))
```

## C. Identifying under a pre-specified minimum specificity of 95% and selecting thresholds with the highest sensitivity.
```{r}
# Bootstrap
boot_thresh <- function(data, index) {
  # Bootstrap sample
  data_ind <- data[index, ]
  # Fit logistic regression
  model_glm_boot <- glm(
    model_term,
    family = binomial,
    data = data_ind
  )
  # Predicted probabilities
  predict_prob <- predict(model_glm_boot, newdata = data_ind, type = "response")
  # ROC curve
  predict_roc <- pROC::roc(response = data_ind$crs_outcome_glm, predictor = predict_prob, quiet = TRUE)
  # Get threshold requiring specificity ≥95%
  roc_coords <- pROC::coords(
    predict_roc,
    x = "all",
    ret = c("threshold", "sensitivity", "specificity"),
    transpose = FALSE
  )
  
  # Keep thresholds achieving ≥95% specificity
  candidate <- roc_coords[
    roc_coords$specificity >= 0.95,
  ]
  
  # Select threshold with highest sensitivity
  optimal_95 <- candidate[
    which.max(candidate$sensitivity),
  ]
  
  specificity95_threshold <- as.numeric(
    optimal_95[["threshold"]]
  )
  
  specificity95_sensitivity <- as.numeric(
    optimal_95[["sensitivity"]]
  )
  
  specificity95_specificity <- as.numeric(
    optimal_95[["specificity"]]
  )
  
  # Return EXACTLY 3 numbers
  c(
    specificity95_threshold = specificity95_threshold,
    specificity95_sensitivity = specificity95_sensitivity,
    specificity95_specificity = specificity95_specificity
  )
}

library(boot)

set.seed(123)
boot_results <- boot(data = dat_df, statistic = boot_thresh, R = 1000)
# boot_results

original_estimates <- boot_results$t0 
calculated_bias <- colMeans(boot_results$t) - boot_results$t0 
bias_corrected_estimates <- original_estimates - calculated_bias 
```

threshold/sensitivity/specificity comparison
```{r}
bind_rows(original_estimates,bias_corrected_estimates, .id = "model") |> 
  mutate(model = case_when(
    model == 1    ~ "Original",
    model == 2    ~ "Bootstrap"
  ))
```

# III. Build nomogram
nomogram() takes the fitted logistic regression model and converts the regression coefficients into a visual point-based prediction.   

Detailed point assignments:
```{r echo = TRUE, class.source= 'fold-hide'}
library(rms)

dd <- datadist(dat_df)
options(datadist = "dd")

model_rms <- lrm(
  crs_outcome_glm ~ 1 + bsln_bmpc_cat25 + bridging_response_prbetter + bsln_ferr_cat400 + ecog_at_ld_cat + bsln_crp_cat05 + cytogenetics,
  data = dat_df,
  x = TRUE,
  y = TRUE
)
# model_rms

nom_original <- nomogram(
  model_rms,
  fun = plogis,
  funlabel = "Predicted Probability of \nSevere Early Toxicity"
)
nom_original
```

Nomogram for prediction of Severe Early Toxicity
```{r, fig.height=6, fig.width=10, echo = TRUE, class.source= 'fold-hide'}
# tiff(
#   "Figures/Nomogram1.tiff",
#   width = 10,
#   height = 8,
#   units = "in",
#   res = 600,
#   compression = "lzw",
#   bg = "white"
# )
plot(nom_original)
# dev.off()

nom <- nomogram(
  model_rms,
  fun = plogis,
  funlabel = "Predicted Probability of \nNo Severe Early Toxicity",
  lp = FALSE, # will remove the linear predictor line in plot
  # fun.at = c(0.01, 0.05, 0.10, 0.20, 0.30, 0.50, 0.70, 0.90), # probabilities appearing on the bottom scale
  abbrev = FALSE
)

# tiff(
#   "Figures/Nomogram_20260918.tiff",
#   width = 9,
#   height = 6,
#   units = "in",
#   res = 600,
#   compression = "lzw",
#   bg = "white"
# )
plot(nom,
     xfrac = 0.35, # horizontal space is reserved for the variable labels
     cex.axis = 0.7, # size of the numbers
     cex.var = 0.8, # size of predictor names on the left
     lmgp = 0.3, # spacing between factors labels and the lines
     col.grid = gray(0.85), # vertical grid lines
     col.conf = gray(0.5),
     tcl = -0.2 # tick marks length - < 0 is point inward
)
# dev.off()
```

